Reduced plasticity and opportunity for selection in terrestrial ectotherm populations under climate change

### 2023-05-14 ms.qmd
Fixed degree symbol

The opportunity for selection, as captured by $lnCVR_{Q_{10}}$, showed a decrease across all habitat types but were especially pronouced in terrestrial and marine ectotherms. Overall, there was a `r mean(t_cvr_mean_ef)`% (95% CI: `r quantile(t_cvr_mean_ef, 0.025)[1]` to `r quantile(t_cvr_mean_ef, 0.975)[1]`, $p_{mcmc}$ = `r pmcmc(t_cvr_mean)`) reduction in variation in physiological rates for terrestrial ectotherms and a `r mean(m_cvr_mean_ef)`% (95% CI: `r quantile(m_cvr_mean_ef, 0.025)[1]` to `r quantile(m_cvr_mean_ef, 0.975)[1]`, $p_{mcmc}$ = `r pmcmc(m_cvr_mean)`) reduction in variation for marine ectotherms when temperatures increase by 10$\deg$C. In contrast, freshwater ectotherms exhibited a much smaller reduction in physiologiocal rate variance at high temperatures (`r mean(f_cvr_mean_ef)`%, 95% CI: `r quantile(f_cvr_mean_ef, 0.025)[1]` to `r quantile(f_cvr_mean_ef, 0.975)[1]`, $p_{mcmc}$ = `r pmcmc(f_cvr_mean)`).

>>>>

The opportunity for selection, as captured by $lnCVR_{Q_{10}}$, showed a decrease across all habitat types but were especially pronouced in terrestrial and marine ectotherms. Overall, there was a `r mean(t_cvr_mean_ef)`% (95% CI: `r quantile(t_cvr_mean_ef, 0.025)[1]` to `r quantile(t_cvr_mean_ef, 0.975)[1]`, $p_{mcmc}$ = `r pmcmc(t_cvr_mean)`) reduction in variation in physiological rates for terrestrial ectotherms and a `r mean(m_cvr_mean_ef)`% (95% CI: `r quantile(m_cvr_mean_ef, 0.025)[1]` to `r quantile(m_cvr_mean_ef, 0.975)[1]`, $p_{mcmc}$ = `r pmcmc(m_cvr_mean)`) reduction in variation for marine ectotherms when temperatures increase by 10$^\circ$C. In contrast, freshwater ectotherms exhibited a much smaller reduction in physiologiocal rate variance at high temperatures (`r mean(f_cvr_mean_ef)`%, 95% CI: `r quantile(f_cvr_mean_ef, 0.025)[1]` to `r quantile(f_cvr_mean_ef, 0.975)[1]`, $p_{mcmc}$ = `r pmcmc(f_cvr_mean)`).
